Automatically Proving Equivalence by Type-Safe Reflection

### 2017-03-31 paper-CICM-17/content/1-introduction.tex
Agaaaaain more fixes

Unfortunately, this straightforward definition is rejected by Idris' type-checker because the types mismatch for both of the two patterns. The result of the first line \code{adc zero zero carry} is expected to have the type \codeL{Binary\ 1\ (plus\ (plus\ c\ 0)\ 0)} but we provide a term of type \code{Binary\ 1\ (plus\ c\ (plus\ 0\ (plus\ 0\ 0)))}.
The problem is even worse for the second case where the expected index is \codeL{(plus\ (plus\ c\ (plus\ bit2\ (plus\ v1\ (plus\ v1\ 0))))\ (plus\ bit\ (plus\ v\ (plus\ v\ 0))))}
while we're trying to provide a term indexed over
\codeL{plus\ vLsb\ (plus\ (plus\ (plus\ vCarry0\ v1)\ v)\ (plus\ (plus\ (plus\ vCarry0\ v1)\ v)\ 0))}.
We know that the definition of \code{adc} we have given is correct, and it has \emph{provably} the expected type, but it does not have it \emph{immediately} or \emph{by reduction} : after full reductions\footnote{In dependently typed theories, the presence of types predicated on values creates the need of using reductions also inside of types}, the expected and provided types are still different, and Idris can not figure out a proof of compatibility on its own. 
If we use provisional definitions[ref], the previous definition can be accepted by the system, but we now have two proof obligations \code{adc\_lemma\_1} and \code{adc\_lemma\_2} demanding proofs of equality between the two types, and they have to be provided by hand --here with a proof script-- :

>>>>

Unfortunately, this straightforward definition is rejected by Idris' type-checker because the types mismatch for both of the two patterns. The result of the first line \code{adc zero zero carry} is expected to have the type \codeL{Binary\ 1\ (plus\ (plus\ c\ 0)\ 0)} but we provide a term of type \code{Binary\ 1\ (plus\ c\ (plus\ 0\ (plus\ 0\ 0)))}.
The problem is even worse for the second case where the expected index is \codeL{(plus\ (plus\ c\ (plus\ bit2\ (plus\ v1\ (plus\ v1\ 0))))\ (plus\ bit\ (plus\ v\ (plus\ v\ 0))))}
while we're trying to provide a term indexed over
\codeL{plus\ vLsb\ (plus\ (plus\ (plus\ vCarry0\ v1)\ v)\ (plus\ (plus\ (plus\ vCarry0\ v1)\ v)\ 0))}.
We know that the definition of \code{adc} we have given is correct, and it has \emph{provably} the expected type, but it does not have it \emph{immediately} or \emph{by reduction} : after full reductions\footnote{In dependently typed theories, the presence of types predicated on values creates the need of using reductions also inside of types}, the expected and provided types are still different, and Idris can not figure out a proof of compatibility on its own. 
If we use provisional definitions~\cite{DBLP:conf/plpv/Brady13}, the previous definition can be accepted by the system, but we now have two proof obligations \code{adc\_lemma\_1} and \code{adc\_lemma\_2} demanding proofs of equality between the two types, and they have to be provided by hand --here with a proof script-- :
